---
title: "Homework 2"
name: Duong (Danny) Nguyen
UNI: dqn2104
output: github_document
editor_options: 
  chunk_output_type: console
---

# Load library

```{r,results=FALSE}
library(tidyverse)
library(moderndive)
library(ggplot2)
```

# Problem 1

```{r,results=FALSE}
data("early_january_weather")
?early_january_weather
```

## Description of the data

This dataset shows weather data on hourly meterological data for LGA, JFK, and EWR for the month of January 2013. This data frame has `r nrow(early_january_weather)` and `r ncol(early_january_weather)` represening hourly measurements of 15 variables. Some of its variables include temperature, humidity, wind direction&speed&gust speed, precipitation,etc. The average temperature is `r mean(early_january_weather$temp)`.

## Scatterplot

```{r,results=FALSE}
plot = 
  ggplot(early_january_weather, aes(x=time_hour, y=temp, color=humid))+
  geom_point() + 
  labs( x = "Time (Hours)",
        y = "Temperature(F)")

plot

ggsave("plot.pdf")
```

### Description of the graph 

The scatterplot shows a non-linear graph between time and temperature. Due to its being an hourly documentation of temperature, it is usual to see this pattern as the temperature tends to go down at night, but rising in the morning. However, overall, we can see an upward trend as it peaks at about 57 degree while its lowest point being 24 degree. There maybe a positive correlation between temperature and humidity as higher temperature leads to higher humidity, but further analysis is needed to conclude this. 

